Regime transition identification for water utilization in river basin developments

### 2020-10-09 tex/main/manuscript.tex
refine the introduction section

% tag 引言第二段
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018, schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 人水系统中的水资源功能
Water have several key functions within a human-water system, the most important of which is supplying for human societies in further developments based on water utilization. 
% 水资源利用 regime shift
However, interplayed human interference, involving water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
\cite{falkenmarkUnderstandingWaterResilience2019}.
% 稳态转换随着社会发展增加
These gradual or abrupt drivers triggered regime shifts as societies' development strengthen their interlinks to water utilization and deepening dependences on them.
% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
% Regime 过渡性的存在
As a result, most large river basins had gone through water utilization regimes of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern. 
% TODO 这里需要安排参考文献，大河流域的发展历程
% 过渡性有助于理解流域存在的问题
Sketching the transition of water utilization regimes, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
% 对过渡性的研究还很少
Despite pervasiveness, there is still lacking of effective method to distinguish the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.

% Tag 引言第三段
% 前人已经从不同维度刻画了人水关系.
Development of societies by using water resources has been going on for at least thousands of years. Although its regime shifts and transition phases are not fully understood yet, features of water utilization has been depicted and studied from different perspectives.
% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
Firstly, water stresses are of increasing importance and concerns because of scarcity.
Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use during the last century, while store of water resource in reservoirs are helpful to relief of
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
Secondly, as the need of industry, services and ecology developments, priority of water utilization changed with. 
Despite a major water utilization of agricultural irrigation dominating most river basins, there are noticeable growths in economy profits of industry or services and their priority in water consumption, leading potential conflicts between different sectors
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
Thirdly, since water distribution and utilization are inherently regional concerns where all regions attempt to develop themselves by economically competitive sectors, configuration also plays as an important aspect.
% 全球总的取水量很少，但缺水地区很多
While only 10\% of available water is withdrawn on global average, about 30\% of population settles in highly water-stressed regions with vary dominated water demands
\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
% 此外，人类活动还在改变这一格局
Human activities further affect this configuration, as positive impacts mostly occur in upper regions whereas aggravated downstream, though most governments are trying to control this situation. 
\cite{veldkampWaterScarcityHotspots2017}. 
% 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: ``How much water resources?'', ``How to use them?'' and ``Used for whom or in where?''.
% 将三种视角结合，就是“水资源利用体系”。
As these dimensions haven't been well integrated by quantitative methods, however, there is still lacking a coherent interpret of regime shifts regard to social development and water utilization.

% tag 引言最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization (Figure~\ref{fig:framework}).
% 使用案例研究
Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes and their shifts in this typical basin of anthropogenic impacts, with change points detection and contribution decomposition methods following.
% 指出发展困局
In addition, combining data analysis, we identify drivers of the regime shifts. 
% 最后总结出一般性框架
Finally, refer to the existing theories, we summarized a universal transition framework of water utilization regimes, which can be a useful guideline for basins to predict development dilemmas and to develop in a coordinated way.

>>>>

% tag 引言第二段
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, whose large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts \cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 人水系统中的水资源功能
Water have several key functions within a human-water system, the most important of which is supplying for human societies in further developments based on water utilization. 
% 水资源利用 regime shift
However, interplayed human interference, involving water withdrawal, dam constructions and water managements have significantly changed water functions and induced changes in water use
\cite{falkenmarkUnderstandingWaterResilience2019}.
% 稳态转换随着社会发展增加
These gradual or abrupt drivers triggered regime shifts as societies' development strengthen their interlinks to water utilization and deepening dependences on them.
% TODO 这里需要安排参考文献，稳态转换的触发方式，随着社会发展更多
% Regime 过渡性的存在
As a result, most large river basins had gone through phases of accelerated exploitation, over-exploitation, and integrated management, for which it is a reasonable assumption that there is a general transition pattern in water utilization. 
% TODO 这里需要安排参考文献，大河流域的发展历程
% 因此，识别水资源利用的稳态变化，并从中寻找一般性的发展模式，有助于理解流域存在的问题
Identifying the regime shifts in water utilization and sketching a general pattern, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.

% 这里删掉的部分
% % 过渡性有助于理解流域存在的问题
% Sketching the transition of water utilization regimes, therefore, can help to understand and predict developing trajectories of basins, which are crucial for integrated management and coordinated development towards sustainability.
% % 对过渡性的研究还很少
% Despite pervasiveness, there is still lacking of effective method to distinguish the water utilization regimes and detect regime shifts, with much fewer attempts to develop theoretical models to explain their transitions as well.

% Tag 引言第三段
% 前人已经从不同维度刻画了人水关系.
Features of water utilization has been depicted and studied from various intertwined perspectives so far.
% 首先，因为水资源的稀缺性和全球用水量的增加，受到最广泛关注的是人类社会面临的水资源压力。
Firstly, water stresses are of increasing importance and concerns because of scarcity.
Greater water utilization stresses had become a major constraint to development, because of significant increment in water withdrawals and larger shares of inflexible water use, while store of water resource in reservoirs are helpful to relief of
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，随着工业迅猛发展和生态建设的需要，社会对水资源的利用的倾向性也发生了转变。
Secondly, as the need of developments, priority of water utilization changed with and there are noticeable growths in economy profits of industry or services and their priority in water use, leading potential conflicts between different sectors
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 最后，由于水的可用性本质上是区域问题，水资源利用的格局也很重要
Thirdly, since development are inherently regional concerns, where heterogeneous regions attempt to develop themselves by economically competitive sectors, configuration of water resources also plays as an important aspect.
% 全球总的取水量很少，但缺水地区很多
As a result, while only 10\% of available water is withdrawn on global average, about 30\% of population settles in severe water-stressed regions for higher level of development
\cite{wadaWedgeApproachWater2014, okiGlobalHydrologicalCycles2006}.
% 总的来说，上述三个维度试图解答与水资源利用有关的三个重要问题 “还有多少水资源可以利用”，“把水资源用在什么”
Taken together, existing researches have evaluated the three dimensions of water resource utilization regarding a series of crucial questions: ``How much water resources?'', ``How to use them?'' and ``Used for whom or in where?''.
% 将三种视角结合，就是“水资源利用体系”。
As these dimensions haven't been well integrated by quantitative methods, however, there is still lacking a coherent interpret of regime shifts regard to social development and water utilization.

% tag 引言最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, by integrating three above mentioned dimensions of water utilization, we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to give a sketch of relationships between human societies and their water utilization (Figure~\ref{fig:framework}).
% 使用案例研究
Then, by applying this index to the Yellow River Basin, China, we analysed water utilization regimes shifts and their drivers in this typical basin of anthropogenic impacts.
% 最后总结出一般性框架
Finally, we proposed a transition phases framework of development echoing to the regime shifts, which can be a useful guideline for basins to predict dilemmas in water utilization and to develop in a coordinated way.
